Plot curve fits

### 2023-01-10 Working Rmds/plot_fits.Rmd
Read in pre-processed data.

```{r}
timestamp <- "2023_01_05"
```

@@

```{r, load_cvt, eval = TRUE}
cvt_data <- fread(paste0("../inst/ext/cvt_data_",
timestamp,
".csv"))
```
List of new_name = old_name to supply for preprocessing data

```{r}
names_list <- list(
  "Compound_Dosed" = "studies.test_substance_name_original",
  "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
  "CAS_Dosed" = "chemicals_dosed.dsstox_casrn",
  "Compound_Analyzed" = "series.analyte_name_original",
  "DTXSID_Analyzed" = "chemicals_analyzed.dsstox_substance_id",
  "CAS_Analyzed" = "chemicals_analyzed.dsstox_casrn",
  "Reference" = "documents_reference.id",
  "Extraction" = "documents_extraction.id",
  "Species" = "subjects.species",
  "Weight" ="subjects.weight_kg",
  "Weight.Units" = NULL,
  "Dose" = "studies.dose_level_normalized_corrected", #note that dose levels were corrected in pulling_oral_iv_data_cvtdb.Rmd
  "Dose.Units" = NULL,
  "Time" = "conc_time_values.time_hr",
  "Time.Units" = NULL,
  "Media" = "series.conc_medium_normalized",
  "Value" = "conc_time_values.conc", #already normalized to mg/L units in CvTdb
  "Value.Units" = NULL,
  "Route" = "studies.administration_route_normalized",
  "LOQ" = "series.loq_normalized", #note that LOQs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
  "Subject" = "subjects.id",
  "N_Subjects" = "series.n_subjects_in_series",
  "Value_SD" = "conc_time_values.conc_sd_normalized" #note that SDs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
  )
```

List of default values for new columns added in preprocessing data

```{r}
defaults_list <- list(
                      "Weight.Units" = "kg",
                      "Dose.Units" = "mg/kg",
                      "Time.Units" = "h",
                      "Value.Units" = "mg/L")
```

For ease of plotting, get the pre-processed, harmonized data:

```{r}
cvt <- preprocess_data(data.set = cvt_data,
                       names_list =names_list,
                       defaults_list =   defaults_list,
                       ratio_conc_to_dose = 1,
                       calc_loq_factor = 0.45,
                       routes_keep = c("po", "iv"),
                       media_keep = c("blood", "plasma"),
                       suppress.messages = FALSE)
cvt <- as.data.table(cvt)

#save pre-processed data
write.csv(cvt,
          paste0("cvt_preprocessed_",
                 timestamp,
          ".csv"))
```

@@

#plot all models
tmp <- mapply(plot_fit,
              DTXSID_in = plot_table$DTXSID,
                     Species_in = plot_table$Species,
              MoreArgs = list(
                     model_in = "all",
                     Analysis_Type_in = "Joint",
                     DF = cvt,
                     pk_fit = pk_fit,
                     n = 101,
                     limit_y_axis = FALSE,
                     log10_scale_y = FALSE,
                     plot_errbars = TRUE,
                     log10_scale_time = FALSE,
                     file_path = "../inst/ext/plots/Joint Analysis/model_all/errbars_naturaly")
                     )

>>>>

```{r}
timestamp <- "2023_01_06"
```

@@

```{r, load_cvt, eval = TRUE}
cvt <- fread("../inst/ext/cvt_preprocessed_2023_01_06.csv")
cvt[, Reference:=as.character(Reference)]
cvt[, Reference_orig:=as.character(Reference_orig)]
```

@@

#plot all models
tmp <- mapply(plot_fit,
              DTXSID_in = plot_table$DTXSID,
                     Species_in = plot_table$Species,
              MoreArgs = list(
                     model_in = "all",
                     Analysis_Type_in = "Joint",
                     DF = cvt,
                     pk_fit = pk_fit,
                     n_interp_time = 10,
                     limit_y_axis = FALSE,
                     log10_scale_y = FALSE,
                     plot_errbars = TRUE,
                     log10_scale_time = FALSE,
                     file_path = "../inst/ext/plots/Joint Analysis/model_all/errbars_naturaly")
                     )
